Query Optimization for Dynamic Imputation

### 2017-03-01 paper/experiments.tex
Update results subsec intro language
paper: widows & orphans
Fix remaining small items

All experiments were run on a single Amazon Web Services EC2 {\tt c4.xlarge} instance, with
four 2.9 GHz Intel Xeon E5--2666 v3 virtual CPUs and 7.5 GiB of main memory, on Debian Linux.

Each query was separately run 200 times in both settings and then

@@

@@

\Cref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error (SMAPE)~\cite{Makridakis2000451} for
\ProjectName{}'s query results when compared to the results of running imputation on the base tables and
executing the query on this cleaned base data \cite{tofallis2015better}. Given that the main datasets used
have no ground truth, this measure indicates how much error is introduced by on-the-fly imputation compared
to imputation on the base tables.

>>>>

@@

All experiments were run on a single Amazon Web Services EC2 {\tt c4.xlarge} instance, with
four 2.9 GHz Intel Xeon E5--2666 v3 virtual CPUs and 7.5 GiB of main memory, on Debian Linux.
Each query with each value of $\alpha$ was run 200 times, after discarding a warm-up period.

@@

\Cref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error (SMAPE)~\cite{Makridakis2000451} for
\ProjectName{}'s query results when compared to the results of running imputation on the base tables and
executing the query on this cleaned base data. Given that the main datasets used
have no ground truth, this measure indicates how much error is introduced by on-the-fly imputation compared
to imputation on the base tables.

### 2017-03-01 paper/relatedwork.tex
paper: more widows & orphans
Fix remaining small items

\subsection{Forecasting and Databases}
Parisi et al.~\cite{parisi2011embedding} introduce the idea of incorporating time-series forecast operators into
databases, along with the necessary relational algebra extensions. Their work explores the theoretical
properties of forecast operators and generalizes them into a family of operators, distinguished by
the type of predictions returned. They highlight the use of forecasting for replacing missing values.
In their follow on work~\cite{parisi2013temporal}, they identify various equivalence and containment
relationships when using forecast operators, which could be used to perform query plan transformations that guarantee the same result. They
explore forecast-first and forecast-last plans, which perform forecasting operations before and after executing all traditional
relational operators, respectively.

>>>>

\subsection{Forecasting and Databases}
\cite{parisi2011embedding} introduce the idea of incorporating time-series forecast operators into
databases, along with the necessary relational algebra extensions. Their work explores the theoretical
properties of forecast operators and generalizes them into a family of operators, distinguished by
the type of predictions returned. They highlight the use of forecasting for replacing missing values.
In their follow on work~\cite{parisi2013temporal}, they identify various equivalence and containment
relationships when using forecast operators, which could be used to perform query plan transformations that guarantee the same result. They
explore forecast-first and forecast-last plans, which perform forecasting operations before and after executing all traditional
relational operators, respectively.
